\TheTitle

### 2017-07-15 paper/background.tex
adding background fixes

Each repository event contains an ordered list of one or more parents,
except the initial commit which has no parents. The parent relationship
points from the current event toward the initial commit.  Commits have a
single parent, while merges will have at least two parents, the parent
on the current branch followed by the branches being merged into the
current branch. Git allows for the merging of multiple branches
simultaneously in octopus merges, where the order of the parents
represents the order that the branches were specified for being merged\footnote{One octopus merge in Linux
  (2cde51fbd0f310c8a2c5f977e665c0ac3945b46d) has 66 parents.}.
A \foxtrot\footnote{See
  \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html}
  for a full description of the issue.} merge occurs when the parent on
the current branch is replaced by a parent from a branch being merged
into the current branch, thus confounding the branch relationships.\dmg{this would benefit from a diagram, since
most people will have no idea what you are talking about.}

The repository events in the DAG are immutable; once a repository event
is created, it can't be changed. \dmg{the next sentences should be
  repository events, not commits} Git allows operations to alter
repository events and re-order them, but this will create a new event
with a new commit hash. This property makes a repository event unable to
record the traversal of merges into the master branch of the repository.
Introducing an additional field to track the path to the master branch
would create a circular dependency between the parent and child. Any
updates to the DAG would modify the commit hashes for all repository
events in the repository. To alleviate this, git provides the command
\verb|git log --children| which traverses the DAG and prints the
inverted edges relationship between events.

>>>>

Each repository event contains an ordered list of one or more parents,
except the initial commit which has no parents. The parent relationship
points from the current event toward the initial commit.  Commits have a
single parent, while merges will have at least two parents, the parent
on the current branch followed by the branches being merged into the
current branch. Git allows for the merging of multiple branches
simultaneously in octopus merges, where the order of the parents
represents the order that the branches were specified for being merged\footnote{One octopus merge in Linux
  (2cde51fbd0f310c8a2c5f977e665c0ac3945b46d) has 66 parents.}.
A \foxtrot\footnote{See
  \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html}
  for a full description of the issue.} merge occurs when the parent on
the current branch is replaced by a parent from a branch being merged
into the current branch, thus confounding the branch relationships.

% TODO: Get a diagram of a foxtrot

The repository events in the DAG are immutable; once a repository event
is created, it can't be changed. Git allows operations to alter
repository events and re-order them, but this will create a new event
with a new commit hash. This property makes a repository event unable to
record the traversal of merges into the master branch of the repository.
Introducing an additional field to track the path to the master branch
would create a circular dependency between the parent and child. Any
updates to the DAG would modify the commit hashes for all repository
events in the repository. To alleviate this, git provides the command
\verb|git log --children| which traverses the DAG and prints the
inverted edges relationship between events.
